---
title: "ARE 212- Problem Set 2"
author: "Samira Siddique"
date: "March 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Read the data into R. Print out the data. Read it. Plot the series and make sure your data are read in correctly.
Make sure your data are sorted by size (kwh). [Hint: Check for obvious typos in the data and if you nd any
x them!]

2. Replicate regression I (page 176) in the paper. (You won't be able to exactly, since the original data contained
an error that has been xed). Your estimate for the price differences will differ slightly, but the R2 will be the
same.

3. Conduct the hypothesis test using constant returns to scale (y = 1) as your null hypothesis. What is the p-
value associated with you test statistic? What is your point estimate of returns to scale? Constant? Increasing?
Decreasing?

4. Plot the residuals against output. What do you notice? What does this potentially tell you from an economic
perspective? Compute the correlation coecient of the residuals with output for the entire sample? What does
this tell you?

5. Nerlove tried to remedy his "residual problem" by running separate models for dierent sized industries. Divide
your sample into 5 subgroups of 29 rms each according to the level of output. Estimate the regression model
again for each group separately. Can you replicate Equations IIA - IIIE? Calculate the point estimates for
returns to scale for each sample. Is there a pattern relating to size of output?

6. Create "dummy variables" for each industry [which you may have done in the previous part]. Interact them with
the output variable to create ve "slope coecients". Run a model, letting the intercept and slope coecient
on output dier across plants, but let the remainder of the coeffcients be pooled across plants. Are there any
noticeable changes in returns to scale from the previous part?

7. Conduct a statistical test comparing the rst model you estimate to the last model you estimated. (Hint: Is
one model a restricted version of the other?). Would separate t-test have given you the same results?

8. To see whether returns to scale declined with output, Nerlove tested a nonlinear specication by including
(ln(y))2 as a regressor. Conduct a statistical test you feel is appropriate to test this hypothesis.
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
